---
title: "Subreddit Analysis"
author: "Michael Puerto"
date: "11/10/2020"
output: 
  html_document:
    toc: true
    code_folding: hide
---

```{r}

library(pacman)
p_load(tidyverse,tidytext,tm,lubridate,stringr, text2vec,jsonlite,widyr,quanteda,visNetwork,igraph,ggraph,DT)



lsf_data = read_csv("C:/Users/macia/Documents/MSIA-19/Git/MSIA-21-/Network Analysis/lsf_data.csv")

lsf_data_comments = read_csv("C:/Users/macia/Documents/MSIA-19/Git/MSIA-21-/Network Analysis/lsf_data_comments.csv")

```


## Data collection

---

### Using Python, R and Bigquery

- Python
  * used to interact with PRAW (The Python Reddit API) that grabbed 'current' posts for link scraping.
  * This data is used in the emote(companion) analysis. 


- R
  * Used to interact with BigqueryR to pull data from the Pushshift reddit dataset which contained historical data from '16. 
  * Collected Reddit posts and Reddit Comments
  * Used to carry out the analysis
  * Used to create this  presentation
  
  
  
## Looking at the data



```{r eval=require('DT')}
DT::datatable(
  head(lsf_data, 3),caption = "LSF Posts: 39k observations, 7 variables",fillContainer = T,width =800 ,height = 1200)

```


<br>

```{r eval=require('DT')}
DT::datatable(head(lsf_data_comments, 3),caption = "LSF Commments: 1.4M Observations, 8 variables",fillContainer = T)

```
